GRB Afterglows In The Multi-Messenger Era

### 2019-01-23 structuredJets.tex
sketched section 6

@@

@@

@@

The mapping between structured jet and refreshed shock (and hence energy injection) models is a two step process.  Firstly, a visual comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes} indicate the identical roles played by $g$ and $k$. Indeed, a stru

@@

@@

@@

>>>>

%
% Update jet Structure models paper.
%

@@

%
% Comment: Add dashed line at 0 to slopes plot.
%

@@

%
% Comment: define tdec, tmin IN THE TEXT.   Add (brief) discussion of light curve phases.
%

@@

There is no single mapping between the structured jet and energy injection or refreshed shock models.  However, a visual comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes} indicate the identical roles played by $g$ and $k$.  Indeed, a simple swap $g \leftrightarrow k$ produces almost identical closure relations.  However, as seen in Tables \ref{tab:slopes} and \ref{tab:refreshSlopes} or

The mapping between structured jet and refreshed shock (and hence energy injection) models is a two step process.   Indeed, a stru

%
% Comment: replace s_3 with s_Omega, s_{1,2} with s_gamma, s_t.
%
% "It is insightful..."
%

@@

%
% Comment: Emphasize this is in "misaligned" case for structured case, but also applies to refreshed shock.  Just use "alpha".
%

%
% Comment: THE JET BREAK *IS* WHEN THE VISIBLE PATCH STOPS GROWING
%

@@

We use the electromagnetic afterglow of GW170817A (GRB170817A?) as an example application of both the analytic and numerical structured jet afterglow models.

Figure \ref{fig:170817Alc} shows the observations in radio, optical, and x-ray bands of the GW170817A afterglow.  No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger (CITE TrojaNature).  Further radio, optical, and x-ray observations showed a steady rising light curve with constant power-law slope until a peak near day 160.  At this point the light curve turned over and began a steep decay that continues to the present (CITE YearInTheLife).

Interpreting the afterglow as arising from a structured jet allows one to quickly draw the following conclusions:
\begin{enumerate}
	\item The spectral slope $\beta = 0.585$ (CITE, +uncertainties) throughout the entire evolution, identifying the relevant spectral regime as G: $\nu_m < \nuobs < \nu_c$, and $p = 2.17$.
	\item The initial rising ($\alpha < 0$) light curve with declining spectrum ($\beta > 0$) identify this as a \emph{misaligned} evolution ($\thobs > \thC$).  Aligned jets may only have a rising light curve when viewed at frequencies below the peak frequency, that is when $\beta < 0$.
	\item The rising light curve maintains $\alpha  = 0.90 \pm 0.06$ (CITE YITL).  Using the closure relations from Table \ref{tab:slopes} we can identify this as the \emph{structured} phase and determine $\geff = 7.5 \pm 0.4$.  If the light curve underwent an \emph{off-axis} phase, it concluded before the afterglow was detected: $\tW < 9$d.  The peak can be identified as the jet-break: $\tb = 164 \pm 12$ d.
	\item In the context of a Gaussian jet, the measurement of $\geff$ leads immediately to $\thobs / \thC = 5.5 \pm 0.2$.
	\item Using the Fong 2015 (CITE Fong 2015) fiducial values of $E_0 \sim 2\times 10^{51}$erg and $n_0 \sim 10^{-2}$cm$^{-3}$ we can use the jet break $\tb$ measurement to determine $\thobs \approx 0.5 \pm 0.2$ rad ($29^\circ \pm 12^\circ$), assuming 1 dex uncertainties on $E_0$ and $n_0$.    This is in agreement with the LIGO measurement $\thobs \approx 28^\circ \pm 15^\circ$ (assuming the SHoES $H_0$).
	\item The combined measurements of $\thobs$ and $\thobs/\thC$ then imply $\thC \approx 0.09 \pm 0.04$ rad ($5^\circ  \pm 2^\circ$).

\end{enumerate}

@@

(-9/2+6p-3g) / (8+g) = a
-9/2+6p-3g = a(8+g)
-9/2+6p-8a = ag + 3g
-9/2+6p-8a = (a + 3)g
g = (-9/2+6p-8a) / (a+3)
